Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-19 prob.tex
prob.tex \subsection{Recover an Interval-valued Born Rule(?)} Added...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantum Probability Spaces}

@@

$\bar{\mu}$ cannot correspond to any quantum probability measure.
Suppose $\mu(P)\in\bar{\mu}(P)$ for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}=1$ and $q_{j}>0$.
However, no pure state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
measure~$\mu$.\qed\end{example}

@@

\yutsung{I think there are two possible approaches to complete the
story.

@@

Another possible approach is to tell everybody: because Gleason's
theorem is an accident, the original way to formulate to a quantum
system as a state vector or density matrix is an accident. If we want
to do things correct, we should work on quantum (real/interval)-valued
probability measure directly. This approach is scratched in section~\ref{sec:QC}.
The problem of this approach is that we need an concrete example to
show it is possible to work on quantum (real/interval)-valued probability
measure directly. For example, we might need to verify tensor product
and quantum teleportation works in this model...}

\section{\label{sec:DQT}(One possible approach) Discrete Quantum Theory}

@@

\section{\label{sec:QC}(Another possible approach) Quantum Computing on Quantum
(Real/Interval)-valued Probability Measures}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Quantum-Probability-Spaces}Quantum Probability Spaces}

@@

Finally, we will prove that $\bar{\mu}$ cannot correspond to any
quantum probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}=1$ and $q_{j}>0$.
However, no pure state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
measure~$\mu$.\qed\end{example}

@@

\yutsung{I think there are three possible approaches to complete
the story.

@@

Another possible approach is to tell everybody: because Gleason's
theorem is an accident, the original way to formulate to a quantum
system as a state vector or density matrix is an accident. If we want
to do things correct, we should work on quantum (real/interval)-valued
probability measure directly. This approach is scratched in section~\ref{sec:QC}.
The problem of this approach is that we need an concrete example to
show it is possible to work on quantum (real/interval)-valued probability
measure directly. For example, we might need to verify tensor product
and quantum teleportation works in this model...

The other approach might be keep going section~\ref{sec:Quantum-Probability-Spaces}...}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:DQT}(One possible approach) Discrete Quantum Theory}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:QC}(Another possible approach) Quantum Computing on Quantum
(Real/Interval)-valued Probability Measures}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }

\subsection{Recover an Interval-valued Born Rule(?)}

Although not all interval-valued probability measure could correspond
to any real-valued probability measure as in theorem~\ref{def:EmptyCoreQuantumInterval-valuedProbability},
it does not mean we could not deduce an interval-valued Born rule.
Notice that Gleason's theorem only says every real-valued probability
measure can correspond to a mixed state by the Born rule, but does
not specify the Born rule should be the only rule which corresponds
a mixed state to a real-valued probability measure. For example, Gleason's
theorem does not rule out the correspondence $\mu_{\phi}^{\prime B}(P)=\melem{0}{P}{0}$
which send every state~$\ket{\phi}$ to the same real-valued probability
measure. If we want to recover the Born rule itself, we need to more
conditions to specify which state corresponds to which real-valued
probability measure.

\begin{thm}Consider\emph{ }$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $.
There is a unique interval-valued Born rule~$\bar{\mu}^{B}:\left\{ \ket{\phi}\in\Hilb\middle|\ip{\phi}{\phi}=1\right\} \rightarrow\left(\events\rightarrow\mathscr{I}\right)$
such that:
\begin{itemize}
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}$ is an interval-valued
probability measure.
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(\proj{\phi}\right)=\necess$.
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(P\right)=\bar{\mu}_{\mathbf{U}\ket{\phi}}^{B}\left(\mathbf{U}P\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\qed\end{thm}
